Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-03-08 answer-to-reviewers.tex

The manuscript proposes a condition-based preventive maintenance policy for multi-component systems. The objective is to minimise certain cost rate by means of scheduling preventive maintenance interventions. The failure probabilities and the residual life distribution are updated in a Bayesian fashion as new information of the system’s evolution is gathered. The components are assumed to fail independently, but they are interrelated and the failure of a single component may have an effect in other surrogate elements.

The problem addressed is important and the methodology well-grounded. However, the manuscript requires some important work before it can be accepted.

The English writing is good. However, the paper needs to be reviewed as some sections lack a proper structure and the argument is hard to follow. In particular Section~5 must be completely rewritten.

\emph{***We rewrote Section~5 according to the reviewer's suggestions.***}

@@

More specific comments are summarised in the two following sections:

\subsection*{Technical comments}

\begin{itemize}
\item The notational choice does not seem to be the most appropriate. The use of $\tnow$ is confusing and makes the reading of the paper cumbersome. I will suggest to use something more direct, as $t_j$, where $j=1,\ldots$ represents the $j$th scheduled intervention. With that choice, the notation $\tau^{\tnow}_*$ can be simplified to $\tau^*_j$ without any loss of generality of information. Moreover, with this notational choice (or a similar one) the expression $t_j=j \delta$ becomes natural and. [sic!]

\emph{***This conflicts with our approach that evaluates the RLD and $\tausnow$ also at the exact times of component failures***}

@@

\emph{***This conflicts with our approach that evaluates the RLD and $\tausnow$ also at the exact times of component failures***}

\item The claim in the first paragraph of Section 5 is a strong one and should be properly proved or, at least, a reference must be provided.

\emph{***unclear which claim exactly he refers to, maybe to
``Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time, $\tausnow$ will typically decrease.'' ???
It will be hard to prove this formally, as $\tausnow$ is a result of an optimization over the re-estimated RLD.
But informally, this is clear: when a component fails, this is taken up by the RLD calculation,
such the probability mass of the RLD is moving closer to $\tnow$,
which leads to $\tausnow$ being closer to $\tnow$ as well.***}

@@

\emph{***unclear which claim exactly he refers to, maybe to
``Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time, $\tausnow$ will typically decrease.'' ???
It will be hard to prove this formally, as $\tausnow$ is a result of an optimization over the re-estimated RLD.
But informally, this is clear: when a component fails, this is taken up by the RLD calculation,
such the probability mass of the RLD is moving closer to $\tnow$,
which leads to $\tausnow$ being closer to $\tnow$ as well.***}

\item In Section 5.1, the authors indicate that if, for a given time $\tnow$, $\tau_*^{\tnow}<\delta$, then a preventive maintenance is triggered. I wonder if it will not be better to wait until $\tau_*^{\tnow}$? Given that $\tau_*^{\tnow}$ is---by definition---the optimal intervention time, it seems that the best action is to intervene precisely at that time.

\emph{***Hm, yes, currently we have that the system is repaired at $\tnow$ when $\tausnow < \delta$.
I could change the simulations to execute repair at time $\tnow + \tausnow$,
but then one needs to check whether there is a component failure (and with it, a system failure)
between time $\tnow$ and $\tnow + \tausnow$, making the policy flow chart even more complex.
If we keep it as it is, we need to explain $\delta$ better as being very small such that repair at $\tnow$ or $\tnow + \tausnow$
do not make a big difference and that without $\delta$, we get a situation like in the paradox of Achilles and the tortoise.}

@@

\emph{***Hm, yes, currently we have that the system is repaired at $\tnow$ when $\tausnow < \delta$.
I could change the simulations to execute repair at time $\tnow + \tausnow$,
but then one needs to check whether there is a component failure (and with it, a system failure)
between time $\tnow$ and $\tnow + \tausnow$, making the policy flow chart even more complex.
If we keep it as it is, we need to explain $\delta$ better as being very small such that repair at $\tnow$ or $\tnow + \tausnow$
do not make a big difference and that without $\delta$, we get a situation like in the paradox of Achilles and the tortoise.}

\item It seems that the authors assume constant preventive and corrective maintenance costs. However, in practice one finds that maintenance costs are often state dependent. Is their model suitable for this? Is it robust to different cost structures? How will their results be affected?

\emph{***We need to add a comment on this in Section~8. It is possible to have costs dependent on time and on system state,
method works in the same way, $\tausnow$ will be more variable then.
Relation to our simplifying assumption that all components are replaced in a maintenance action?***}

\item Throughout the manuscript it is assumed that the survival signature, $\Phi$, is a given parameter of the problem and no further details are given. Even though this may be correct for any real life application of their methodology, for the sake of completeness I will suggest to either include the complete version of Table 1 (maybe as an appendix) or to provide a closed form of the corresponding survival signature for their toy example.

\emph{***Upon re-inspection of Table~1, we have found some errors that we have now corrected,
and would like to apologize for the confusion that the errors may have caused.
We now exemplarily show how $\Phi$ is obtained for the case of $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
and give an explanation on how the omitted rows in Table~1 can be easily determined by the reader.\\
{\scriptsize
(1) Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~1, then the corresponding $\Phi$ is $0$.\\
(2) Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~1, then the corresponding $\Phi$ is $1$.}\\
Also add complete table in Appendix, or formula for $\Phi$ based on structure function???***}

@@

\smallskip

\emph{***Upon re-inspection of Table~1, we have found some errors that we have now corrected,
and would like to apologize for the confusion that the errors may have caused.
We now exemplarily show how $\Phi$ is obtained for the case of $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
and give an explanation on how the omitted rows in Table~1 can be easily determined by the reader.\\
{\scriptsize
(1) Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~1, then the corresponding $\Phi$ is $0$.\\
(2) Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~1, then the corresponding $\Phi$ is $1$.}\\
Also add complete table in Appendix, or formula for $\Phi$ based on structure function???***}

\item Five subsequent operation cycles seems to be a rather short simulation horizon. I will suggest the authors to extend their analysis to, at least, 20-25 cycles.

\emph{***??? We can do more subsequent operation cycles,
but I would think more repetitions (say, 100 instead of 20) would be better.
Maybe emphasize that we use a single-cycle optimization criterion,
not a renewal-based criterion that indeed holds only for a large number of cycles?
Also, for many cycles the difference between CBM-cpu and CBM-epu will decrease.***}

\item Beside the didactical advantages of the small example, the authors should consider a more realistic framework for testing their model. Results should be provided for a larger scale simulation exercise.

\emph{***We decided to use the simple example also in the simulation study to keep the paper shorter,
but another, more complex system would be possible, only extending computation times.
But what should this more complex system look like? We would need to think of a realistic example...***}
\end{itemize}

### 2017-03-08 answer-to-reviewers.tex

\emph{***unclear which claim exactly he refers to, maybe to
``Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time, $\tausnow$ will typically decrease.'' ???
It will be hard to prove this formally, as $\tausnow$ is a result of an optimization over the re-estimated RLD.
But informally, this is clear: when a component fails, this is taken up by the RLD calculation,
such the probability mass of the RLD is moving closer to $\tnow$,
which leads to $\tausnow$ being closer to $\tnow$ as well.***}

\item In Section 5.1, the authors indicate that if, for a given time $\tnow$, $\tau_*^{\tnow}<\delta$, then a preventive maintenance is triggered. I wonder if it will not be better to wait until $\tau_*^{\tnow}$? Given that $\tau_*^{\tnow}$ is---by definition---the optimal intervention time, it seems that the best action is to intervene precisely at that time.

\smallskip

\emph{***Hmmm, yes, currently we have that the system is repaired at $\tnow$ when $\tausnow < \delta$.
I could change the simulations to execute repair at time $\tnow + \tausnow$,
but then one needs to check whether there is a component failure (and with it, a system failure)
between time $\tnow$ and $\tnow + \tausnow$, making the policy flow chart even more complex.
If we keep it as it is, we need to explain $\delta$ better as being very small such that repair at $\tnow$ or $\tnow + \tausnow$
do not make a big difference and that without $\delta$, we get a situation like in the paradox of Achilles and the tortoise.}

@@

\emph{***We need to add a comment on this in Section~8. It is possible to have costs dependent on time and on system state,
method works in the same way, $\tausnow$ will be more variable then.
Relation to our simplifying assumption that all components are replaced in a maintenance action?***}

\item Throughout the manuscript it is assumed that the survival signature, $\Phi$, is a given parameter of the problem and no further details are given. Even though this may be correct for any real life application of their methodology, for the sake of completeness I will suggest to either include the complete version of Table 1 (maybe as an appendix) or to provide a closed form of the corresponding survival signature for their toy example.

\smallskip

\emph{***Upon re-inspection of Table~1, we have found some errors that we have now corrected,
and would like to apologize for the confusion that these errors may have caused.
We now exemplarily show how $\Phi$ is obtained for the case of $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
and give an explanation on how the omitted rows in Table~1 can be easily determined by the reader.\\
{\scriptsize
(1) Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~1, then the corresponding $\Phi$ is $0$.\\
(2) Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~1, then the corresponding $\Phi$ is $1$.}\\
Also add complete table in Appendix, or formula for $\Phi$ based on structure function???
Also note here that there is software to calculate $\Phi$?***}

@@

\emph{***We decided to use the simple example also in the simulation study to keep the paper shorter,
but another, more complex system would be possible, only extending computation times.
But what should this more complex system look like? We would need to think of a realistic example...***}
\end{itemize}

\subsection*{General Comments}

\begin{itemize}
\item The authors claim that no degradation signal is used for monitoring the system’s state. However, they mention that the status of the components can be monitored continuously. How can this be done? This question becomes more important when the authors mention that certain inspections (which reveal the status of the systems) can be conducted periodically. This seems to be in contradiction with the continuous monitoring mentioned above. Could the authors be so kind to clarify this?

\emph{***??? We seem to have confused the reviewer thoroughly.
We need to clarify that we do not use a \textbf{usual} degradation signal, like vibration measurements.
But we do get a continuous signal from the components of the system, telling us whether they work or not.
I need to check again if we say somewhere that we do inspections periodically, which is not true.
We re-evaluate the RLD periodically (and additionally at times of component failures).***}

@@

\emph{***??? We seem to have confused the reviewer thoroughly.
We need to clarify that we do not use a \textbf{usual} degradation signal, like vibration measurements.
But we do get a continuous signal from the components of the system, telling us whether they work or not.
I need to check again if we say somewhere that we do inspections periodically, which is not true.
We re-evaluate the RLD periodically (and additionally at times of component failures).***}

\item The fourth paragraph in Section 1, starting with “In this paper…” must be rewritten. Their argument is not clear and it may seem contradictory; e.g. “no degradation signal for the system is available” and later “each component sends a binary signal”. At the end, it is not clear how information is collected.

\emph{***Again, we need to clarify that we do not use a \textbf{usual} degradation signal for the \textbf{system as a whole},
but that the component status information (working or not) can be seen as a special kind of multivariate system degradation signal.
I would also do not call our approach ``inspection-based'', as we now do in that paragraph.}

@@

\emph{***Again, we need to clarify that we do not use a \textbf{usual} degradation signal for the \textbf{system as a whole},
but that the component status information (working or not) can be seen as a special kind of multivariate system degradation signal.
I would also do not call our approach ``inspection-based'', as we now do in that paragraph.}

\item The definition of an operational cycle in the first paragraph of page 3 seems to be in conflict with the one provided elsewhere in the manuscript, in particular page 11, Section 5.

\emph{p.~3: ``where an operational cycle starts with a new system,
and ends after this system has been replaced by an as good as new system''\\
Section~5: ``An operational cycle begins with system start-up,
and ends when either preventive maintenance is carried out, or a failure of the system occurs,
with subsequent corrective maintenance.''\\
*** I don't quite see the conflict, maybe mention in Sec~5 directly after that sentence that maintenance means replacing the whole system?
And write on p.~3 ``begins with the start-up of a new system'', or even
``An operational cycle spans the time between two consecutive system maintenance actions / replacements.
We thus optimize the unit cost rate calculated over the time since the last system replacement.''
?***}

@@

\emph{p.~3: ``where an operational cycle starts with a new system,
and ends after this system has been replaced by an as good as new system''\\
Section~5: ``An operational cycle begins with system start-up,
and ends when either preventive maintenance is carried out, or a failure of the system occurs,
with subsequent corrective maintenance.''\\
*** I don't quite see the conflict, maybe mention in Sec~5 directly after that sentence that maintenance means replacing the whole system?
And write on p.~3 ``begins with the start-up of a new system'', or even
``An operational cycle spans the time between two consecutive system maintenance actions / replacements.
We thus optimize the unit cost rate calculated over the time since the last system replacement.''
?***}

\item I suggest the authors to define all the acronyms on their first use. For example, CBM is used throughout the text, but never defined; and RDL is used from page 2, but not defined until page 3 (in Section 2).

\emph{CBM was defined in the first line of Section~1, where we wrote ``CBM (condition-based maintenance)''.
We now write ``condition-based maintenance (CBM)'' instead.
We are sorry that we did define RLD too late, and now define it at the first use on page~2.***}
